### 2020-02-08 all_models.tex
updating tex

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|}
\hline
%    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
%    & $\langle\log\Vert\mathbf{W}\Vert_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\langle\hat{\alpha}=\alpha\log\lambda_{max}\rangle$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
Series        & $\log\Vert\cdot\Vert_{F}$ & $\log\Vert\cdot\Vert_{\infty}$ & $\hat{\alpha}$ & $\log\Vert\cdot\Vert^{\alpha}_{\alpha}$ \\
\hline
$R^{2}$ (mean) & 0.63 &0.55 &0.64 &0.64 \\
$R^{2}$ (std)  & 0.34 &0.36 &0.29 &0.30 \\
\hline
$MSE$ (mean)   & 4.54 &9.62 &3.14 &2.92 \\
$MSE$ (std)    & 8.69 &23.06 &5.14 &5.00 \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of linear regression fits for different average log norm metrics across 5 computer vision datasets, 17 Architectures, covering 168 (out of 309) different pretrained DNNs.  We only conclude regressions for architecturs with 4 or more data points \charles{and which are postively correlated with the test error?}.  These results can be readily reproduced using the Google Colab notebooks accompanying thie paper~\cite{notebooks}}
\label{table:results}
\end{table}

>>>>

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|}
\hline
%    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
%    & $\langle\log\Vert\mathbf{W}\Vert_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\langle\hat{\alpha}=\alpha\log\lambda_{max}\rangle$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
Series        & $\log\Vert\cdot\Vert_{F}$ & $\log\Vert\cdot\Vert_{\infty}$ & $\hat{\alpha}$ & $\log\Vert\cdot\Vert^{\alpha}_{\alpha}$ \\
\hline
$R^{2}$ (mean) & 0.63 &0.55 &0.64 &0.64 \\
$R^{2}$ (std)  & 0.34 &0.36 &0.29 &0.30 \\
\hline
$MSE$ (mean)   & 4.54 &9.62 &3.14 &2.92 \\
$MSE$ (std)    & 8.69 &23.06 &5.14 &5.00 \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of linear regression fits for different average log norm metrics across 5 computer vision datasets, 17 Architectures, covering 168 (out of 309) different pretrained DNNs.  We only conclude regressions for architecturs with 4 or more data points, and which are postively correlated with the test error.  These results can be readily reproduced using the Google Colab notebooks (see Appendix)}
\label{table:results}
\end{table}

### 2020-02-08 cv_models.tex
updating tex

\begin{figure}[t]
    \centering
    \subfigure[ Frobenius Norm, VGG ]{
        %\includegraphics[width=5cm]{img/VGG_lognorm_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_lognorm_accs.png}
        \label{fig:vgg-fnorm}
    }
    %\qquad
    \subfigure[ Spectral Norm, VGG ]{
        %\includegraphics[width=4.9cm]{img/VGG_spectralnorm_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_spectralnorm_accs.png}
        \label{fig:vgg-snorm}
    }
    %\qquad
    \subfigure[ Weighted Alpha, VGG ]{
        %\includegraphics[width=4.9cm]{img/VGG_alpha_weighted_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_alpha_weighted_accs.png}
        \label{fig:vgg-walpha}
    }
    %\qquad
    \subfigure[ $\alpha$-Norm, VGG ]{
        %\includegraphics[width=4.9cm]{img/VGG_logpnorm_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_logpnorm_accs.png}
        \label{fig:vgg-pnorm}
    }
    \caption{Comparison of quality metrics versus reported test accuracy for pretrained VGG models, trained on ImageNet, available in pyTorch.  
             XXX Plots will be updated and replaced. 
             \michael{Figures are unreadable, can we make fonts bigger, etc.}
            }
    \label{fig:vgg-metrics}
\end{figure}

@@

    \subfigure[ ResNet, $\alpha$-Norm ]{
        %\includegraphics[width=4.2cm]{img/ResNet_logpnorm_accs.png}
        \includegraphics[width=4.0cm]{img/ResNet_logpnorm_accs.png}
        \label{fig:resnet-accuracy}
    }
    %\qquad
    \subfigure[ ResNet-1K, $\alpha$-Norm ]{
        %\includegraphics[width=4.5cm]{img/ResNet-1K_logpnorm_accs.png}
        \includegraphics[width=4.0cm]{img/ResNet-1K_logpnorm_accs.png}
        \label{fig:resnet1k-accuracy}
    }
    %\qquad
    \subfigure[ DenseNet, $\alpha$-Norm ]{
        %\includegraphics[width=4.4cm]{img/DenseNet_logpnorm_accs.png}
        \includegraphics[width=4.0cm]{img/DenseNet_logpnorm_accs.png}
        \label{fig:densenet-accuracy}
    }
    \caption{$\alpha$-Norm versus reported Top1 Error for  ResNet, ResNet-1K, and DenseNet models. The corresponding results for VGG are shown in Figure~\ref{fig:vgg-pnorm}.  }
    \label{fig:cv2-accuracy}
\end{figure}

@@

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|c|}
%\begin{tabular}{|l|c|c|c|c|c|}
\hline
%   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
% Series & \#Models   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
        &        & Log                   & Log                        & Weighted       & Log                                 \\
        & Num.   & $\Vert\cdot\Vert_{F}$ & $\Vert\cdot\Vert_{\infty}$ & $\hat{\alpha}$ & $\Vert\cdot\Vert^{\alpha}_{\alpha}$ \\
 Series & Models & Metric                & Metric                     & Metric         & Metric                              \\
\hline
 VGG       &  6 & 0.56 & 0.53 & 0.48          & \textbf{0.42}  \\
 ResNet    &  5 & 0.9  & 1.4  & \textbf{0.61} & 0.66           \\
 ResNet-1K & 19 & 2.4  & 3.6  & \textbf{1.8}  & 1.9            \\
 DenseNet  &  4 & 0.3  & 0.26 & \textbf{0.16} & 0.21           \\
\hline
\end{tabular}
\end{center}
\caption{RMSE (smaller is better) for linear fits of quality metrics to Reported Top1 Test Error for pretrained models in each architecture series.  VGG, ResNet, and DenseNet were pretrained on ImageNet, and ResNet-1K was pretrained on ImageNet-1K. 
\michael{Are the numbers in this table stale; if they get updated, then we need to modify the test at at least two places, on actual numbers and on what is best.}
}
\label{table:cv-models}
\end{table}

Figure~\ref{fig:cv2-accuracy} plots the 
%overall best performing (i.e., 
Log $\alpha$-Norm
%) 
metric for the full ResNet, ResNet-1K, and DenseNet series.
(A much more detailed set of plots, including the behavior of all four methods on each of the series, is available at \cite{XXX-WEB-LINK}.)
Here, the Log $\alpha$-Norm is much better that the Log Frobenius/Spectral norm metrics (although, as Table~\ref{table:cv-models} shows, it is actually slightly worse than the Weighted Alpha metric).
Notice also that ResNet series, which has been trained on the full ImageNet dataset, has an RMSE of $0.66$, whereas the ResNet-1K series, which has been trained on the much smaller ImageNet-1K dataset, also correlated wells, but has a much larger RMSE of $1.9$.

See Table~\ref{table:cv-models} for a summary of results for Top1 Accuracies for all four metrics on all four model series.
Similar results (not shown) are obtained for the Top5 Accuracies.
Overall, for the the ResNet, ResNet-1K, and DenseNet series, all metrics perform relatively well, the Log $\alpha$-Norm metric performs second best, and the Weighted Alpha metric performs best. 
These model series are all well-trodden, and our results indicate that norm-based metrics and PL-based metrics can both distinguish among ``good-better-best'' models, with PL-based metrics performing somewhat better.

\paragraph{Layer Analysis: Correlation Flow in CV Models.}

We can learn much more about a pretrained model by going beyond average values to examining quality metrics for each layer weight matrix, $\mathbf{W}$, as a function of depth (or layer id).  % in the network. 
%The most interesting results are seen when we 
For example, we can 
plot (just) the PL exponent, $\alpha$,%
\footnote{That is, here we consider just $\alpha$ for each layer, i.e., not $\hat{\alpha}$ or $\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}$.} 
as a function of depth.
%
See Figure~\ref{fig:3models-alpha-layers}, which plots $\alpha$ for each layer (the first layer corresponds to data, the last layer to labels) for the least accurate (shallowest) and most accurate (deepest) model in each of the VGG (without BatchNormalization), ResNet-1K, and DenseNet series.
(Again, much more detailed set of plots is available at \cite{XXX-WEB-LINK}; but note that the corresponding layer-wise plots for Frobenius and Spectral norms are much less interesting than the results we present here.)

@@

    \subfigure[ VGG ]{
        %\includegraphics[width=4.5cm]{img/VGG_fnl_alpha_depth.png} 
        \includegraphics[width=4.0cm]{img/VGG_fnl_alpha_depth.png} 
                \label{fig:vgg-alpha-layers}
    }
    %\qquad
    \subfigure[ ResNet-1K ]{
        %\includegraphics[width=4.5cm]{img/ResNet_fnl_alpha_depth.png} 
        \includegraphics[width=4.0cm]{img/ResNet_fnl_alpha_depth.png} 
        \label{fig:resnet-alpha-layer}
    }
    %\qquad
    \subfigure[ DenseNet ]{
        %\includegraphics[width=4.5cm]{img/DenseNet_fnl_alpha_depth.png} 
        \includegraphics[width=4.0cm]{img/DenseNet_fnl_alpha_depth.png} 
        \label{fig:densenet-alpha-layer}
    }
    \caption{Layer Analysis. 
             PL exponent $\alpha$ versus layer id, for VGG, ResNet-1K, and DenseNet models.  
             (Y axes on each plot are different.)  
             ResNet-1K exhibits different and much more stable behavior across layers.
             This contrasts with how VGG gets gradually worse in deeper layers and how DenseNet is worse and much more erratic.  
             We interpret this in the text as quantifying a \emph{correlation flow} across the layers.  
            }
    \label{fig:3models-alpha-layers}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \subfigure[ Frobenius Norm, VGG ]{
        %\includegraphics[width=5cm]{img/VGG_lognorm_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_lognorm_accs.png}
        \label{fig:vgg-fnorm}
    }
    %\qquad
    \subfigure[ Spectral Norm, VGG ]{
        %\includegraphics[width=4.9cm]{img/VGG_spectralnorm_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_spectralnorm_accs.png}
        \label{fig:vgg-snorm}
    }
    %\qquad
    \subfigure[ Weighted Alpha, VGG ]{
        %\includegraphics[width=4.9cm]{img/VGG_alpha_weighted_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_alpha_weighted_accs.png}
        \label{fig:vgg-walpha}
    }
    %\qquad
    \subfigure[ $\alpha$-Norm, VGG ]{
        %\includegraphics[width=4.9cm]{img/VGG_logpnorm_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_logpnorm_accs.png}
        \label{fig:vgg-pnorm}
    }
    \caption{Comparison of average log Norm empirical quality metrics versus reported test accuracy for pretrained VGG models (with and without BatchNormalization), trained on ImageNet, available in pyTorch (v1.x).  Metrics fit by linear regression, RMSE reported. }
    \label{fig:vgg-metrics}
\end{figure}

@@

    \subfigure[ ResNet, $\alpha$-Norm ]{
        %\includegraphics[width=4.2cm]{img/ResNet_logpnorm_accs.png}
        \includegraphics[width=4.0cm]{img/ResNet_logpnorm_accs.png}
        \label{fig:resnet-accuracy}
    }
    %\qquad
    \subfigure[ ResNet-1K, $\alpha$-Norm ]{
        %\includegraphics[width=4.5cm]{img/ResNet-1K_logpnorm_accs.png}
        \includegraphics[width=4.0cm]{img/ResNet-1K_logpnorm_accs.png}
        \label{fig:resnet1k-accuracy}
    }
    %\qquad
    %\subfigure[ DenseNet, $\alpha$-Norm ]{
    %    %\includegraphics[width=4.4cm]{img/DenseNet_logpnorm_accs.png}
    %    \includegraphics[width=4.0cm]{img/DenseNet_logpnorm_accs.png}
    %    \label{fig:densenet-accuracy}
    %}
    \caption{Comparison of the avergage $\alpha$-Norm empirical quality metric $\langle\log\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}\rangle$ 
versus reported Top 1 reported Test Accuracy for the ResNet and ResNet-1K pretrained (pyTorch) models. }
%, and DenseNet models. }The corresponding results for VGG are shown in Figure~\ref{fig:vgg-pnorm}.  }
    \label{fig:cv2-accuracy}
\end{figure}

@@

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|c|}
%\begin{tabular}{|l|c|c|c|c|c|}
\hline
 Series    &\#   & $\log\langle\Vert\mathbf{W}\Vert_{F}\rangle$ & $\log\langle\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\log\langle\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
 VGG       &  6 & 0.56 & 0.53 & 0.48          & \textbf{0.42}  \\
 ResNet    &  5 & 0.9  & 1.4  & \textbf{0.61} & 0.66           \\
 ResNet-1K & 19 & 2.4  & 3.6  & \textbf{1.8}  & 1.9            \\
 DenseNet  &  4 & 0.3  & 0.26 & \textbf{0.16} & 0.21           \\
\hline
\end{tabular}
\end{center}
\caption{RMSE (smaller is better) for linear fits of quality metrics to Reported Top1 Test Error for pretrained models in each architecture series.  VGG, ResNet, and DenseNet were pretrained on ImageNet, and ResNet-1K was pretrained on ImageNet-1K. 
\michael{Are the numbers in this table stale; if they get updated, then we need to modify the test at at least two places, on actual numbers and on what is best.}
}
\label{table:cv-models}
\end{table}

See Table~\ref{table:cv-models} for a summary of results for Top1 Accuracies for all four metrics on for the VGG, ResNet, and DenseNet series.
Similar results (not shown) are obtained for the Top5 Accuracies.
Overall, for the the ResNet, ResNet-1K, and DenseNet series, all metrics perform relatively well, the Log $\alpha$-Norm metric performs second best, and th\
e Weighted Alpha metric performs best.
These model series are all well-trodden, and our results indicate that norm-based metrics and PL-based metrics can both distinguish among ``good-better-bes\
t'' models, with PL-based metrics performing somewhat better.

Notice that the DenseNet series,  only has 4 data points.  In our larger analysis, in Section~\ref{sxn:all} we only include series with 5 or more models.
For completemnss and reproducibility here, the DenseNet Log $\alpha$-Norm plot is given in the Appendix.

\paragraph{Variations in Data Set Size}
We want to point out, in particular, how the empirical log Norm metrics vary with data set size.
Figure~\ref{fig:cv2-accuracy} plots and compares the 
Log $\alpha$-Norm
metric--the best performing metric--for the full ResNet, trained on the full ImageNet dataset, against the ResNet-1K, which has been trained on a much smaller ImageNet-1K data set.
%(A much more detailed set of plots, including the behavior of all four methods on each of the series, is available at \cite{XXX-WEB-LINK}.)
Here, the Log $\alpha$-Norm is much better that the Log Frobenius/Spectral norm metrics (although, as Table~\ref{table:cv-models} shows, it is actually slightly worse than the Weighted Alpha metric).
The ResNet series, has an RMSE of $0.66$, whereas the ResNet-1K series also shows good correlation, but has a much larger RMSE of $1.9$.
As expected, the higher quality data set shows a better fit, even with less data points.

\paragraph{Layer Analysis: Correlation Flow in CV Models.}
We can learn much more about a pretrained model by going beyond average values to examining quality metrics for each layer weight matrix, $\mathbf{W}$, as a function of depth (or layer id).  % in the network. 
%The most interesting results are seen when we 
For example, we can 
plot (just) the PL exponent, $\alpha$,%
\footnote{That is, here we consider just $\alpha$ for each layer, i.e., not $\hat{\alpha}$ or $\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}$.} 
as a function of depth.
%
See Figure~\ref{fig:3models-alpha-layers}, which plots $\alpha$ for each layer (the first layer corresponds to data, the last layer to labels) for the least accurate (shallowest) and most accurate (deepest) model in each of the VGG (without BatchNormalization), ResNet-1K, and DenseNet series.
(Again, much more detailed set of plots is available at \cite{XXX-WEB-LINK}; but note that the corresponding layer-wise plots for Frobenius and Spectral norms are much less interesting than the results we present here.)

@@

    \subfigure[ VGG ]{
        %\includegraphics[width=4.5cm]{img/VGG_fnl_alpha_depth.png} 
        \includegraphics[width=4.0cm]{img/VGG_fnl_alpha_depth.png} 
                \label{fig:vgg-alpha-layers}
    }
    %\qquad
    \subfigure[ ResNet ]{
        %\includegraphics[width=4.5cm]{img/ResNet_fnl_alpha_depth.png} 
        \includegraphics[width=4.0cm]{img/ResNet_fnl_alpha_depth.png} 
        \label{fig:resnet-alpha-layer}
    }
    %\qquad
    \subfigure[ DenseNet ]{
        %\includegraphics[width=4.5cm]{img/DenseNet_fnl_alpha_depth.png} 
        \includegraphics[width=4.0cm]{img/DenseNet_fnl_alpha_depth.png} 
        \label{fig:densenet-alpha-layer}
    }
    \caption{Correlation Flow: Power Law exponent $\alpha$ versus layer id, for the least and the most accurate
      models in VGG (a), ResNet (b), and DenseNet (c) series (VGG without BatchNorm, and the Y axes on each plot are different.)  
             Figure (d) displays the ResNet models (b), zoomed in to $alpha\in[1,5]$, and with the layer ids overlaid on the X-axis, to
             allow a more detailed analysis for the most strongly correlated layers.
             Notuece that ResNet152 exhibits different and much more stable behavior across layers
             This contrasts with how both VGG models gradually worsen in deeper layers and how the DenseNet models are much more erratic.  
            }
    \label{fig:3models-alpha-layers}
\end{figure}

### 2020-02-08 nlp_models.tex
updating tex

In this section, we examine quality metrics described in Section~\ref{sxn:methods} for several NLP model architectures.
%
%In particular, 
Within the past two years, nearly 100 open source, pre-trained NLP DNNs based on the revolutionary Transformer architecture have emerged.
These include variants of BERT, Transformer-XML, GPT, etc.
%
The Transformer architectures consist of blocks of so-called Attention layers, containing two large, Feed Forward (Linear) weight matrics~\cite{Attn2017}. 
In contrast to smaller pre-Activation maps arising in Cond2D layers, Attention matrices are significantly larger.
In general, we have found that they have larger $\alpha$ PL exponents.
Based on HT-SR Theory, 
%(in particular, the interpretation of values of $\alpha \sim 2$ as modeling systems with good correlations over many size scales~\cite{BouchaudPotters03, SornetteBook}), 
this suggests that these models fail to successfully capture many of the correlations in the data (relative to their size) and thus are substantially \emph{under}-trained.
%
More generally, compared to the CV models of Section~\ref{sxn:cv},
modern NLP models have larger weight matrices and display different spectral properties, and 
%, both in terms of their architecture (e.g., wheter there are convolutions) as well as how they are used (e.g., whether one uses prediction error or perplexity).
thus, they provide a very different test for our empirical quality metrics.

@@

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|c|}
\hline
%   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha Norm \\
% Series & \#Layers   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
        &        & log                   & log                        & Weighted       & log                                 \\
        & Num.   & $\Vert\cdot\Vert_{F}$ & $\Vert\cdot\Vert_{\infty}$ & $\hat{\alpha}$ & $\Vert\cdot\Vert^{\alpha}_{\alpha}$ \\
 Series & Layers & Metric                & Metric                     & Metric         & Metric                              \\
\hline
GPT & 49 & 1.64  & 1.72 & 7.01 & 7.28 \\
GPT2-small & 49 & 2.04  & 2.54& 9.62 & 9.87 \\
GPT2 medium & 98 & 2.08 & 2.58& 9.74 & 10.01 \\
GPT2 large & 146 & 1.85 & 1.99& 7.67 & 7.94 \\
GPT2 xl & 194 & 1.86 & 1.92 & 7.17 & 7.51 \\
\hline
\end{tabular}
\end{center}
\caption{Average value for the Average log Norm metrics and the Weighted Alpha metric for pretrainnd OpenAI GPT and GPT2 models.  }
\label{table:nlp}
\end{table}

@@

\begin{figure}
    \centering
    \subfigure[PL exponent ($\alpha$)]{
        %\includegraphics[width=5cm]{img/GPT-alpha-hist.png}
        \includegraphics[width=4.0cm]{img/GPT-alpha-hist.png}
        \label{fig:GPT-alpha-hist}
       }
    %\qquad
    \subfigure[log Spectral Norm]{
        %\includegraphics[width=5cm]{img/GPT-snorm-hist.png}
        \includegraphics[width=4.0cm]{img/GPT-snorm-hist.png}
        \label{fig:GPT-snorm-hist}
       }
   \caption{Comparison of PL exponents, $\alpha$, and log Spectral Norms, 
$(\log\Vert\mathbf{W}\Vert_{\infty})$, for the OpenAI GPT and GPT2 (small) pretrained models.}
\label{fig:GPT-hist}
\end{figure}

@@

    \subfigure[PL exponent ($\alpha$)]{
        %\includegraphics[width=4.5cm]{img/GPT-alpha-depth.png}
        \includegraphics[width=4.0cm]{img/GPT-alpha-depth.png}
        \label{fig:gpt-alpha-layer}
    }
    %\qquad
    \subfigure[log Spectral Norm]{
        %\includegraphics[width=4.5cm]{img/GPT-snorm-depth.png}
        \includegraphics[width=4.0cm]{img/GPT-snorm-depth.png}
        \label{fig:gpt-snorm-layer}
    }
    %\qquad
    \subfigure[log Alpha Norm]{
        %\includegraphics[width=4.5cm]{img/GPT-pnorm-depth.png}
        \includegraphics[width=4.0cm]{img/GPT-pnorm-depth.png}
        \label{fig:gpt-pnorm-layer}
    }
    \caption{Comparison of Correlation Flow and Spectral Norm for OpenAI GPT and GPT2   }
    \label{fig:gpt-alpha-layers}
\end{figure}

\paragraph{GPT2: small, medium, large, xl}

We now look across the series of increasingly improving GPT2 models, (i.e. ``good, better, best''), 
by examining both the PL exponent $\alpha$, as well as the various log Norm metrics.  
In general, as we move from GPT2-small to GPT2-xl, 
the histograms for both $\alpha$ exponents and the log Norm metrics downshift from larger to smaller values. 
See Figure \ref{fig:gpt2-histograms}, which shows the histograms over the layer weight matrics
for fitted $\alpha$, and the log Spectral Norm
 $(\log\Vert\mathbf{W}\Vert_{\infty})$  
and log Alpha Norm
 $(\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha})$ 
metrics.

We see that the average $\alpha$ decreases with increasing model size, although the differences are less noticible 
between the differing ``good, better, best'' GTP2 models than between the ``good vs bad'' GPT2 and GPT models.
Unlike GPT, however, the layer (log) Spectral Norms $(\log\vert\mathbf{W}\Vert_{\infty})$ 
and (log) Alpha Norms $(\log\vert\mathbf{W}\Vert_{\alpha}^{\alpha})$
behave more as expected for GPT2 layers, with the larger models, consistently having smaller norms. 
\michael{Clarify.}\charles{???}
Likewise, Figure \ref{fig:gpt2-snorm-hist} shows decreasing average log Spectral Norms with the larger models.  
As expected, the norm metrics can indeed distinguish among ``good, better, best'' models
among a series well trained models.

@@

    \subfigure[PL exponent ($\alpha$)]{
        %\includegraphics[width=4.5cm]{img/GPT2_all_alpha_hist.png}
        \includegraphics[width=4.0cm]{img/GPT2_all_alpha_hist.png}
        \label{fig:gpt2-alpha-hist}
    }
    %\qquad
    \subfigure[log Spectral Norm]{
        %\includegraphics[width=4.5cm]{img/GPT2*_all_spectralnorm_hist.png}
        \includegraphics[width=4.0cm]{img/GPT2*_all_spectralnorm_hist.png}
        \label{fig:gpt2-snorm-hist}
    }
    %\qquad
    \subfigure[log Alpha Norm]{
        %\includegraphics[width=4.5cm]{img/GPT2_all_logpnorm_hist.png}
        \includegraphics[width=4.0cm]{img/GPT2_all_logpnorm_hist.png}
        \label{fig:gpt2-pnorm-hist}
    }
    \caption{PL exponents ($\alpha$), log Spectral norm, and log Alpha norm for different size models in the GPT2 architecture series.  (The log Spectral norm histogram omits the first 2 layers, corresponding to the embedding layer, as these are normalized differently and have anamolously large values.)}
    \label{fig:gpt2-histograms}
\end{figure}

>>>>

In this section, we examine quality metrics described in Section~\ref{sxn:methods} for several NLP model architectures.
%
%In particular, 
Within the past two years, nearly 100 open source, pre-trained NLP DNNs based on the revolutionary Transformer architecture have emerged.
These include variants of BERT, Transformer-XML, GPT, etc.
%
The Transformer architectures consist of blocks of so-called Attention layers, containing two large, Feed Forward (Linear) weight matrics~\cite{Attn2017}. 
In contrast to smaller pre-Activation maps arising in Cond2D layers, Attention matrices are significantly larger.
In general, we have found that they have larger $\alpha$ PL exponents.
Based on HT-SR Theory, 
%(in particular, the interpretation of values of $\alpha \sim 2$ as modeling systems with good correations over many size scales~\cite{BouchaudPotters03, SornetteBook}), 
this suggests that these models fail to successfully capture many of the correlations in the data (relative to their size) and thus are substantially \emph{under}-trained.
%
More generally, compared to the CV models of Section~\ref{sxn:cv},
modern NLP models have larger weight matrices and display different spectral properties, and 
%, both in terms of their architecture (e.g., wheter there are convolutions) as well as how they are used (e.g., whether one uses prediction error or perplexity).
thus, they provide a very different test for our empirical quality metrics.

@@

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|c|}
\hline
%   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha Norm \\
% Series & \#Layers   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
        &        & log                   & log                        & Weighted       & log                                 \\
        & Num.   & $\Vert\cdot\Vert_{F}$ & $\Vert\cdot\Vert_{\infty}$ & $\hat{\alpha}$ & $\Vert\cdot\Vert^{\alpha}_{\alpha}$ \\
 Series & Layers & Metric                & Metric                     & Metric         & Metric                              \\
\hline
GPT & 49 & 1.64  & 1.72 & 7.01 & 7.28 \\
GPT2-small & 49 & 2.04  & 2.54& 9.62 & 9.87 \\
\hline
GPT2 medium & 98 & 2.08 & 2.58& 9.74 & 10.01 \\
GPT2 large & 146 & 1.85 & 1.99& 7.67 & 7.94 \\
GPT2 xl & 194 & 1.86 & 1.92 & 7.17 & 7.51 \\
\hline
\end{tabular}
\end{center}
\caption{Average value for the Average log Norm metrics and the Weighted Alpha metric for pretrainnd OpenAI GPT and GPT2 models.  }
\label{table:nlp}
\end{table}

@@

\begin{figure}
    \centering
    \subfigure[Power law exponent ($\alpha$)]{
        \includegraphics[width=4.0cm]{img/GPT-alpha-hist.png}
        \label{fig:GPT-alpha-hist}
       }
    %\qquad
    \subfigure[Spectral Norm $(\log\Vert\mathbf{W}\Vert_{\infty})$]{
        \includegraphics[width=4.0cm]{img/GPT-snorm-hist.png}
        \label{fig:GPT-snorm-hist}
       }
   \caption{Comparison of PL exponents, $\alpha$, and log Spectral Norms, 
$(\log\Vert\mathbf{W}\Vert_{\infty})$, for the OpenAI GPT and GPT2 (small) pretrained models.}
\label{fig:GPT-hist}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \subfigure[Power Law exponent $(\alpha)$]{
        \includegraphics[width=4.0cm]{img/GPT-alpha-depth.png}
        \label{fig:gpt-alpha-layer}
    }
    \subfigure[Spectral Norm $(\log\Vert\mathbf{W}\Vert_{\infty})$]{
        \includegraphics[width=4.0cm]{img/GPT-snorm-depth.png}
        \label{fig:gpt-snorm-layer}
    }
    \caption{Comparison of Correlation Flow and Spectral Norm for OpenAI GPT and GPT2   }
    \label{fig:gpt-alpha-layers}
\end{figure}

\paragraph{GPT2: medium, large, xl} 
We now look across the series of increasingly improving GPT2 models, (i.e. ``good, better, best''), 
by examining both the PL exponent $\alpha$, as well as the various log Norm metrics.  
In general, as we move from GPT2-small to GPT2-xl, 
the histograms for both $\alpha$ exponents and the log Norm metrics downshift from larger to smaller values. 
See Figure \ref{fig:gpt2-histograms}, which shows the histograms over the layer weight matrics
for fitted $\alpha$, and the log Spectral Norm
 $(\log\Vert\mathbf{W}\Vert_{\infty})$  
and log Alpha Norm
 $(\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha})$ 
metrics.

We see that the average $\alpha$ decreases with increasing model size, although the differences are less noticible 
between the differing ``good, better, best'' GTP2 models than between the ``good vs bad'' GPT2 and GPT models.
Unlike GPT, however, the layer (log) Spectral Norms $(\log\vert\mathbf{W}\Vert_{\infty})$ 
and (log) Alpha Norms $(\log\vert\mathbf{W}\Vert_{\alpha}^{\alpha})$
behave more as expected for GPT2 layers, with the larger models, consistently having smaller norms. 
Likewise, Figure \ref{fig:gpt2-snorm-hist} shows decreasing average log Spectral Norms with the larger models.  
As expected, the norm metrics can indeed distinguish among ``good, better, best'' models
among a series well trained models.

@@

    \subfigure[PL exponent ($\alpha$)]{
        \includegraphics[width=4.0cm]{img/GPT2*_fnl_alpha_hist.png}
        \label{fig:gpt2-alpha-hist}
    }
    %\qquad
    %%\subfigure[log Spectral Norm]{
    %    \includegraphics[width=4.0cm]{img/GPT2*_fnl_spectralnorm_hist.png}
    %    \label{fig:gpt2-snorm-hist}
   % }
    %\qquad
    \subfigure[log Alpha Norm]{
        \includegraphics[width=4.0cm]{img/GPT2*_fnl_logpnorm_hist.png}
        \label{fig:gpt2-pnorm-hist}
    }
    \caption{PL exponents ($\alpha$), log Spectral norm $(\log\Vert\mathbf{W}\Vert_{\infty})$, and log Alpha norm $(\log\Vert\mathbf{X}\Vert_{\alpha}^{\alpha})$ for different size models in the GPT2 architecture series.  (Plots omit the first 2 (embedding) layers, because they are normalized differently giving anamolously large values.)}
    \label{fig:gpt2-histograms}
\end{figure}

?
